Figures and results for main manuscript

### 2020-10-14 analysis/reports/manuscript_main.Rmd
headers for links

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         s0 > 1,
         !singletons,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
```

@@

ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
  geom_point(alpha = .01) +
  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
  theme_bw() +
  scale_color_viridis_d() +
  ggtitle("Communities by S and N")

@@

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  geom_vline(xintercept = 95, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")

ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
 geom_histogram(bins = 100) +
  geom_vline(xintercept = 5, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")

@@

overall_skew_results <- all_di %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(dat) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  filter(simpson_unique > 20) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(dat) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results <- left_join(overall_skew_results, overall_simpson_results)

@@

overall_skew_results2 <- all_di %>%
  mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(fia_yn) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results2 <- all_di %>%
  filter(simpson_unique > 20) %>%
   mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(fia_yn) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2)

@@

@@

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100)

ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100)

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         s0 > 1,
         !singletons,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
    Dataset = ifelse(Dataset == "fia", "Forest Inventory and Analysis", Dataset),
        Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
        Dataset = ifelse(Dataset == "mcdb", "Mammal Community DB", Dataset),
        Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
        Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))
```

@@

ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
  geom_point(alpha = .1) +
  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
  theme_bw() +
  scale_color_viridis_d() +
  ggtitle("Communities by S and N") +
  xlab("Log species richness (S)") +
  ylab("Log total abundance (N)")

ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
  geom_point(alpha = .05) +
  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
  theme_bw() +
  scale_color_viridis_d() +
  ggtitle("Communities by S and N") +
   facet_wrap(vars(Dataset), scales = "free") +
  theme(legend.position = "bottom")
  # geom_vline(xintercept = log(40)) +
  # geom_hline(yintercept = log(1000))

@@

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  geom_vline(xintercept = 95, color = "red") +
  theme_bw() +
  facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Skewness, all sites") +
  xlab("Percentile rank of observed skewness value relative to feasible set") +
  ylab("Number of communities")

ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
 geom_histogram(bins = 100) +
  geom_vline(xintercept = 5, color = "red") +
  theme_bw() +
  facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Evenness, all sites") +
  xlab("Percentile rank of observed evenness value relative to feasible set") +
  ylab("Number of communities")

@@

overall_skew_results <- all_di %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  filter(simpson_unique > 20) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
         "Number of communities analyzed for skewness" = nsites_skew,
         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
         "Number of communities analyzed for evenness" = nsites_even)

@@

overall_skew_results2 <- all_di %>%
   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results2 <- all_di %>%
  filter(simpson_unique > 20) %>%
   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
   rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
         "Number of communities analyzed for skewness" = nsites_skew,
         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
         "Number of communities analyzed for evenness" = nsites_even)

@@

# 95 intervals by size of FS

@@

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100) +
  ylim(0,1)+
  xlab("Log number of elements in the feasible set") +
  ylab("Narrowness of the distribution of sampled skewness values")

ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100) +
  ylim(0, 1)+
  xlab("Log number of elements in the feasible set") +
  ylab("Narrowness of the distribution of sampled evenness values")
```

# 95 intervals by dataset

```{r}

ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(vars(Dataset), scales = "free_y") +
    xlab("Narrowness of the distribution of sampled skewness values") +
  ylab("Number of communities")

ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
geom_histogram() +
  theme_bw() +
facet_wrap(vars(Dataset), scales = "free_y") +
    xlab("Narrowness of the distribution of sampled evenness values") +
  ylab("Number of communities")
